A pipeline to analyse time-course gene expression data

### 2019-08-30 scripts/manuscript.Rmd

```{r echo=FALSE, results="hide", message=FALSE}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(knitr)
library(kableExtra)
library(BiocStyle)
library(biomaRt)

@@

EAP:

- I got an error in installation script for  packages:

```
epurdom-0:2019timecourse-rnaseq-pipeline epurdom$ Rscript scripts/install.R
Loading required package: devtools
Loading required package: usethis
Loading required package: ggfortify
Loading required package: ggplot2
Loading required package: kableExtra
Error in contrib.url(repos, "source") : 
  trying to use CRAN without setting a mirror
Calls: install.packages -> contrib.url
In addition: Warning message:
In library(package, lib.loc = lib.loc, character.only = TRUE, logical.return = TRUE,  :
  there is no package called ‘kableExtra’
Execution halted
```

@@

We note that we could have time course data on either a single condition (to
identify genes changing over time) or
time course data on multiple conditions (such as the influenza dataset we are
considering), which will alter slightly the types of questions we are
interested in. 
In what follows, we will focus on the situation
where we have multiple conditions. **EAP: Any reason one and not the other.
Maybe should change this sentence**

@@

```{r echo=FALSE}
kable(contrasts, col.names="Contrasts")
```
**EAP: Not sure if `kable` is better than just printout?**

Then run the differential expression analysis on all of those timepoints
jointly using the function `DE_timepoints`.

@@

```{r echo=FALSE}
kable(weekly_de_analysis[1:10, 1:6 ],digits=3)
```

@@

```{r echo=FALSE}
kable(
    head(log_fold_change_timepoints[, colnames(log_fold_change_timepoints)[1:5]]),
    format = "latex")
```

@@

colnames(pathways) = c("Pathway", "Percentage", "Adj. p-value")
pathways["Percentage"] = pathways["Percentage"] * 100
kable(pathways[1:10, ], "latex", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```

@@

kable(go_terms_enriched[1:15, ], "latex", escape=F, digits=4)  %>%
    kable_styling("striped", full_width=TRUE) 
```

>>>>

```{r echo=FALSE, results="hide", message=FALSE}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(knitr)
library(BiocStyle)
library(biomaRt)
library(kableExtra)

@@

@@

Time course data can either be on a single condition (to identify genes
changing over time) or or on multiple conditions (such as the influenza
dataset we are considering), which will alter slightly the types of questions
we are interested in.

@@

```{r echo=FALSE}
kable(contrasts, "latex", col.names="Contrasts", booktabs=TRUE)
```
Then run the differential expression analysis on all of those timepoints
jointly using the function `DE_timepoints`.

@@

```{r echo=FALSE}
kable(weekly_de_analysis[1:10, 1:6 ], "latex", digits=3, booktabs=TRUE)

@@

```{r echo=FALSE}
kable(
    head(log_fold_change_timepoints[, colnames(log_fold_change_timepoints)[1:5]]),
    format="latex",
    booktabs=TRUE)
```

@@

colnames(pathways) = c("Pathway", "Percentage", "Adj. p-value")
pathways["Percentage"] = pathways["Percentage"] * 100
kable(pathways[1:10, ], format="latex", escape=F, digits=4, booktabs=TRUE)
```

@@

kable(go_terms_enriched[1:15, ], format="latex", escape=F, digits=4, booktabs=TRUE)
```
